Changelog

### 2021-05-24 changelog.tex
Updates from Overleaf

It is possible to extend the quantification part to include other side-channel signals. The key is to model the noises (e.g., Sound, CPU usages, EM signals) properly. In my dissertation, we assume that an attacker can have a noise-free observation. While a noise-free observation is possible for some address-based side-channel attacks, the assumption is too ideal for many other side-channel attacks. The good news is that there are some mature methods in information theory to model the noises (e.g., Gaussian noise). The noisy-channel coding theorem provides a computable method to estimate the information can be reliably transferred between the source (confidential data) and the destination (attackers). From a research project aspect, I hope to have a stronger motivation before starting the project. 
\item \textbf{A bits vs. Q bits. Lower bounds?
       Improve the presentation
       Make the comparison more meaningful
       Etc.}

>>>>

It is possible to extend the quantification part to include other side-channel signals. The key is to model the noises (e.g., Sound, CPU usages, EM signals) properly. In my dissertation, we assume that an attacker can have a noise-free observation. While a noise-free observation is possible for some address-based side-channel attacks, the assumption is too ideal for many other side-channel attacks. The good news is that there are some mature methods in information theory to model the noises (e.g., Gaussian noise). The noisy-channel coding theorem provides a computable method to estimate the information can be reliably transferred between the source (confidential data) and the destination (attackers). From a research project aspect, I hope to have a stronger motivation before starting the project. 
\item \textbf{A bits vs. Q bits. Lower bounds?
       Improve the presentation
       Make the comparison more meaningful
       Etc.}
       \textbf{}
It is hard to understand Entropy. There is a rumor about entropy between John von Neumann and Claude Shannon. When Shannon developed the concept of information theory, he did not have a good idea to name the measurement of uncertainty in a system. Neumann told Shannon, ``You should call it entropy, for two reasons. In the first place your uncertainty function has been used in statistical mechanics under that name, so it already has a name. \textbf{In the second place, and more important, nobody knows what entropy really is, so in a debate you will always have the advantage.}''
